\section{Evaluation} \label{sec:evaluation}

We make the following claims about our system:

\begin{enumerate}

	\item On read workloads where the working set fits in the cache, Vinyl
	      approaches the performance of a local SSD mounted over NVMeoF with SPDK.

	\item We achieve high write performance in all metrics, including IOPS,
	      throughput, and latency.

	\item We can scale with the number of clients independently of the backend,
	      as we serve reads from cache instead of the backend.

\end{enumerate}

To test the above claims, we use a combination of synthetic microbenchmarks,
primarily FIO, and real-world workloads, primarily Filebench. We also compare

\subsection{Environment}

All experiments were run on a 6-machine cluster, 4 of which hosted Ceph OSDs, 1
hosted the gateway, and another hosted the client. All hosts ran unmodified
Ubuntu 22.04 with the Linux 5.15.0-89-generic kernel, had dual-socket Intel Xeon
E5-2660 v2 CPUs and 128 GiB of DDR3-1600 RAM, and were connected over 40GbE
Emulex OneConnect Skyhawk NICs.

The Ceph instance ran on Ceph Quincy 17.2.6, and consists of two primary pools:
a SSD pool backed by 16 Samsung P1635a 1.6TB SSDs, and a HDD pool backed by 48
Seagate Constellation.2 ST91000640SS 1TB HDDs.

Unless otherwise mentioned, VMs are plain QEMU VMs running unmodified Ubuntu
22.04 server images. The images were obtained by running the unattended install
on the Ubuntu server image distribution with most options unchanged.

\subsection{Microbenchmarks}

We present a variety of Fio microbenchmarks to demonstrate the performance of
the disk. All Fio benchmarks were run with a fixed random seed to ensure
repeatability.

\subsubsection{Writes}

As explained above, Vinyl is optimised for writes. \isaac{compare:}

- our write iops to rbd on ssd

- latency v concurrency/qd (choose one)

- we used 10 year old hardware, so we get 10 year old results

\subsubsection{Reads}

- show (hopefully) linear scaling of num clients v total iops

- mention how close we get to saturating the speed/iops of the equivalent
  spdk mounted on local nvme


\subsection{Filebench}
